---
title: "Project 1: Weighted Dice"
output: html_notebook
---

## The very Basics

A die has six sides

## 1.1 The R User Interface

Type things in the command line, or in R chunks. 

```{r interface_1_1}

1 + 1

100:129

```

### Exercise 1.1 Magic with Numbers

```{r ex_1_1}

x <-  8

x <- x + 2

x <- x * 3

x <- x - 6

x <- x / 3

x
```

## 1.2 Objects

```{r obj_1_2}

die <- 1:6

die

ls()

die ^ die

die + 1:4

die %*% die

die %o% die

```

## 1.3 Functions

```{r func_1_3}

mean(die)

sample(die, size = 2)

sample(size = 1, x = die)

```

### 1.3.1 Sample with Replacement

```{r}

sample(die, size = 7)

sample(die, size = 4, replace = TRUE)

dice <- sample(die, size = 2, replace = TRUE)

```

## 1.4 Writing Your Own Functions

Make it repeatable

### 1.4.1 The Function Constructor

Make sure your function returns something

Call the function with (), see the definition without using ()

```{r func_1_4}

roll <- function() { 
  die <- 1:6
  dice <- sample(die, size = 2, replace = TRUE)
  sum(dice)
}

roll()

roll()
```

## 1.5 Arguments

```{r args_1_5}

roll2 <- function(bones = 1:6) {
  dice <- sample(bones, size = 2, replace = TRUE)
  sum(dice)
}

roll2(bones = 1:4)

roll2(1:10)

roll2()

```

## 1.6 Scripts

Scripts are good

## 1.7 Summary

Functions, arguments, scripts.

Dice, Playing Cards, Slot Machines